GSA Work Patterns

### 2023-09-28 04. Analysis/scripts/04-04-reporting-summary-slides.Rmd
Update 04-04-reporting-summary-slides.Rmd

Hybrid work has become widespread over the past three years, however, little is known about GSA employee work patterns.

This information can be used to develop and tailor technologies, spaces, and strategies to support hybrid and distributed models of work so that employees are engaged, perform at their best, and remain focused on mission delivery.

@@

*What technologies and solutions does the federal workforce need to improve effectiveness in a more responsive remote work setting?*

@@

```{r}
p_1 <- 
  prep_d_05 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  facet_wrap(facets = vars(gsa_sso), nrow = 1) +
  labs(title = "Percent of working pattern group by office") +
  ylab("Percent of working pattern group") +
  scale_y_continuous(labels = scales::percent) +
  oescolorrrs::scale_fill_oes() +
  oescolorrrs::scale_color_oes() +
  theme_light() +
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5,
                              size = 13),
    axis.title.y = element_text(size = 8),
    axis.title.x = element_blank()
    )

>>>>

-   Hybrid work has become widespread over the past three years, however, little is known about GSA employee work patterns.

-   This information can be used to develop and tailor technologies, spaces, and strategies to support hybrid and distributed models of work so that employees are engaged, perform at their best, and remain focused on mission delivery.

@@

> *What technologies and solutions does the federal workforce need to improve effectiveness in a more responsive remote work setting?*

@@

```{r}
p_1 <- 
  prep_d_05 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  facet_wrap(facets = vars(gsa_sso), nrow = 1) +
  labs(title = "Percent of working pattern group by office") +
  ylab("Percent of working pattern group") +
  scale_y_continuous(labels = scales::percent) +
  oescolorrrs::scale_fill_oes() +
  oescolorrrs::scale_color_oes() +
  theme_light() +
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5,
                              size = 13),
    axis.title.y = element_text(size = 8),
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 6)
    )
